Efficient pedigree recording for fast population genetics simulation

### 2018-01-04 forwards_paper.tex
SLiM2 -> SLiM 2

Modern computing power easily allows simulations of birth, death and reproduction
in a population having even hundreds of millions of individuals.
However, if our interest lies in the resulting genetic patterns of variation
-- and often, the point of such simulations is to compare to real data --
then such simulations must record each individual's genome.
As samples of most species' genomes harbor tens or hundreds of millions of variant sites,
naively carrying full genotypes for even modest numbers of individuals through a simulation
becomes quickly prohibitive.
To make matters worse,
a population of size $N$ must be simulated across many multiples of $N$ generations
to produce stable genetic patterns \citep{wright1931evolution, wakeley2005coalescent}.
Because of this computational burden, even the fastest simulation frameworks such as
SLiM2~\citep{haller2017flexible} and fwdpp~\citep{fwdpp}
can ``only'' simulate tens of megabases of sequence in tens of thousands of individuals
for tens of thousands of generations, and there are still near-order-of-magnitude performance differences between these
implementations~\citep{haller2017flexible}.
In practice, current state-of-the-art simulation software may take on the order of
weeks to simulate models of large genomic regions without selection~\citep{fwdpp,Hernandez2015-wf},
and existing simulation engines differ in how efficiently they
calculate fitnesses in models with selection~\citep{fwdpp}.
These population and region sizes are still substantially short of whole genomes
(hundreds to thousands of megabases)
for many biological population sizes of interest.

>>>>

Modern computing power easily allows simulations of birth, death and reproduction
in a population having even hundreds of millions of individuals.
However, if our interest lies in the resulting genetic patterns of variation
-- and often, the point of such simulations is to compare to real data --
then such simulations must record each individual's genome.
As samples of most species' genomes harbor tens or hundreds of millions of variant sites,
naively carrying full genotypes for even modest numbers of individuals through a simulation
becomes quickly prohibitive.
To make matters worse,
a population of size $N$ must be simulated across many multiples of $N$ generations
to produce stable genetic patterns \citep{wright1931evolution, wakeley2005coalescent}.
Because of this computational burden, even the fastest simulation frameworks such as
SLiM 2~\citep{haller2017flexible} and fwdpp~\citep{fwdpp}
can ``only'' simulate tens of megabases of sequence in tens of thousands of individuals
for tens of thousands of generations, and there are still near-order-of-magnitude performance differences between these
implementations~\citep{haller2017flexible}.
In practice, current state-of-the-art simulation software may take on the order of
weeks to simulate models of large genomic regions without selection~\citep{fwdpp,Hernandez2015-wf},
and existing simulation engines differ in how efficiently they
calculate fitnesses in models with selection~\citep{fwdpp}.
These population and region sizes are still substantially short of whole genomes
(hundreds to thousands of megabases)
for many biological population sizes of interest.
